---
title: "RDA_Contaminants~Microbioma"
author: "Elena Baños Lara"
date: "29/4/2022"
output:
  html_document:
    theme: readable
    toc: yes
editor_options:
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::include_graphics
options(width = 50)
```

# Opening a new project:
## Necessary libraries:
```{r, message=FALSE, warning=FALSE}
 library(vegan)
# library(scales)
# library(RColorBrewer)
# library(VennDiagram)
 library(gplots)
 library(ggplot2)
# library(ggpubr)
# library(car)
# library(pairwiseAdonis)
# library(ggVennDiagram)
# library(ggplot2)
# library(eulerr)
 library(devtools)
# library(wrapr)
# library(tidyr)
 library(dplyr)
 library(stringr)
library(tidyr)
 library(reshape)
 library(reshape2)
# library(data.table)
# devtools::install_github("pmartinezarbizu/pairwiseAdonis/pairwiseAdonis")
# library(pairwiseAdonis)
# library(tibble)
# library(tidyverse)
# library(dtplyr)
# install.packages("rlang")
# library(rlang)
library("clusterSim")
#library("BiodiversityR")
#library("ggrepel")
#library("ggforce")
#library("data.table")

#devtools::install_github("gavinsimpson/ggvegan")
```

## RDA
RDA: combines regression and PCA, it is an extension of regression analysis to model multivariate response data. RDA computes axes that are linear combinations of the explanatory variables (in order of which explain the most variation of the species matrix). The axes are orthogonal to eachother (i.e. right angles). It is constrained because you are directly testing the influence of explanatory variables.
```{r}
# Fes el dataset bo
setwd("E:/styela/Molecular/Microbioma/microbioma")


pollutans <- read.table("pollutants_rda.txt", header = TRUE, sep = "\t")
pollutans <- pollutans[c(2:55),]

as.data.frame(pollutans)

pollutants <- data.Normalization(pollutans[,c(2:10)], type = "n1", normalization = "column")
#samples <-read.table("asv_taxonomy_april2020_rda.txt", header = TRUE, sep = "\t")

```

####PCA biplot

```{r}
env_PCA <- princomp(pollutants, cor = F)
summary(env_PCA)
tissue <- pollutans$TISSUE
stage <- pollutans$STAGE
pop <- pollutans$POP



env_PCA_plot <- as.data.frame(env_PCA$scores)
mycol <- c("#EC7063","#F4D03F","#85C1E9")  


pdf("PCA_pollutants_loadings.pdf", width=4, height=4)
screeplot(env_PCA, type = "barplot")
dev.off()

PCA_loadings <- env_PCA$loadings
#write.table(PCA_loadings, file="PCA_pol_loadings.txt", sep = "\t")
PCA_loadings <- read.table("PCA_pol_loadings.txt", header = TRUE, sep = "\t")
rownames(PCA_loadings) <- PCA_loadings$X
PCA_loadings <- PCA_loadings[,c(2:10)]


pdf("RDA_nomespol_1vs2.pdf", width = 7, height = 6)
ggplot(data = env_PCA_plot, aes(x = Comp.1, y = Comp.2))+
  geom_point(data = env_PCA_plot, size = 4, aes(color=tissue, shape=pop, fill=stage, alpha=1), stroke = 1.5)+
  geom_segment(data = PCA_loadings, aes(x = 0, xend = 4*Comp.1, y = 0, yend = 4*Comp.2),
               arrow = arrow(length = unit(0.3, "cm")), colour = "steelblue", cex=1) +
  geom_hline(yintercept = 0, lty = "dotted", color="grey", cex=1) +    geom_vline(xintercept = 0, lty = "dotted", color="grey", cex=1) +
  geom_text(data = PCA_loadings, aes(x= 4.5*Comp.1, y = 4.5*Comp.2, label = rownames(PCA_loadings)), 
            size = 5, hjust = 0.5)+
  #geom_text(data = prdav, aes(x = RDA1, y = RDA2, label = rownames(prdav)), 
  #         size = 2.5, col = "black", hjust = 1.2)+
  theme( legend.position="none", 
         panel.grid.minor = element_blank(), 
         panel.grid.major = element_blank(),
         panel.background = element_rect(fill = "transparent", colour = NA))+
  scale_fill_manual(values=mycol, labels=c("Tunic","Gill","Water"))+
  scale_shape_manual(values=c(25,23,21)) +
  scale_color_manual(values=c("#DB7093","#815c97","steelblue")) +
  theme_classic()+
  #labs(x = paste("RDA2 (", round(summary(sty.rda)$cont$importance[2,2]*100, 2), "%)", sep = ""), y = paste("RDA3 (", round(summary(sty.rda)$cont$importance[2,3]*100, 2), "%)", sep = ""))+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  theme(axis.text = element_text(colour = "black", size = 12, face = "bold")) +
  theme(axis.title = element_text(size = 16, colour = "black", family = "Helvetica", face = "bold"))   
dev.off()


pdf("RDA_nomespol_2vs3.pdf", width = 7, height = 6)
ggplot(data = env_PCA_plot, aes(x = Comp.2, y = Comp.3))+
  geom_point(data = env_PCA_plot, size = 4, aes(color=tissue, shape=pop, fill=stage, alpha=1), stroke = 1.5)+
  geom_segment(data = PCA_loadings, aes(x = 0, xend = 4*Comp.2, y = 0, yend = 4*Comp.3),
               arrow = arrow(length = unit(0.3, "cm")), colour = "steelblue", cex=1) +
  geom_hline(yintercept = 0, lty = "dotted", color="grey", cex=1) +    geom_vline(xintercept = 0, lty = "dotted", color="grey", cex=1) +
  geom_text(data = PCA_loadings, aes(x= 4.5*Comp.2, y = 4.5*Comp.3, label = rownames(PCA_loadings)), 
            size = 5, hjust = 0.5)+
  #geom_text(data = prdav, aes(x = RDA1, y = RDA2, label = rownames(prdav)), 
  #         size = 2.5, col = "black", hjust = 1.2)+
  theme( legend.position="none", 
         panel.grid.minor = element_blank(), 
         panel.grid.major = element_blank(),
         panel.background = element_rect(fill = "transparent", colour = NA))+
  scale_fill_manual(values=mycol, labels=c("Tunic","Gill","Water"))+
  scale_shape_manual(values=c(25,23,21)) +
  scale_color_manual(values=c("#DB7093","#815c97","steelblue")) +
  theme_classic()+
  #labs(x = paste("RDA2 (", round(summary(sty.rda)$cont$importance[2,2]*100, 2), "%)", sep = ""), y = paste("RDA3 (", round(summary(sty.rda)$cont$importance[2,3]*100, 2), "%)", sep = ""))+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  theme(axis.text = element_text(colour = "black", size = 12, face = "bold")) +
  theme(axis.title = element_text(size = 16, colour = "black", family = "Helvetica", face = "bold"))   
dev.off()


```
